---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- `devtools::build_readme()` -->

# degreedays

<!-- badges: start -->
<!-- badges: end -->

The goal of degreedays is to download heating degree days from weather stations
throughout Germany from DWD Climate Data Center (CDC) and provide some
convenience functions.

Data set description:

Recent monthly degree days according to VDI 3807 for Germany, quality
control not completed yet, version v19.3, last accessed: 2021-12-02.

More information may be found on the [opendata-server](https://opendata.dwd.de/climate_environment/CDC/derived_germany/techn/monthly/heating_degreedays/hdd_3807/recent/DESCRIPTION_derivgermany_techn_monthly_heating_degreedays_hdd_3807_recent_en.pdf).


## Installation

You can install the development version of degreedays from GitHub.

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("BirgerNi/degreedays")
```


## Usage

You can download the whole data set with `download_dwd_data`.

```{r example, eval = FALSE}
library(degreedays)
df <- download_dwd_data()
df
```

```{r, echo=FALSE}
library(magrittr)
library(degreedays)
df <- readr::read_rds(file = "data_test/dwd.rds")
df
```


You may want to convert data to tsibble and keep only complete or almost complete data sets.

```{r}
tidy_hdd(df, threshold = 0.95)
```


Calculate the monthly mean for a given period with `calc_monthly_mean()`.

```{r}
df %>%
  tidy_hdd(threshold = 0.95) %>%
  calc_monthly_mean(from = 2006, to = 2020)
```

